The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-11-27 Paper.Rmd
reply to editted Data section : still need to discus

\noindent We used datasets that pertain to multiple fields and levels of organization within or related to ecology, including environmental, species-trait, phenological, population, community, and ecosystem functioning data. Copula structure describing the relationship between atmospheric weather variables such as X and Y has been examined previously in the meteorological literature (e.g., REF). We therefore examined environmental variables from the soil instead, using the Rapid Carbon Assessment database (RaCA; @Wills2014).

@@

The database comprises measurements of soil organic carbon and total soil nitrogen (milligrams C or N per m$^{2}$ of soil surface) 
<!--***DAN: Shya, this used to say Mg C, but what is Mg? Do you mean mg for miligram? I have written it out, please check and correct if necessary. Also, I added per m^2 of soil surface, please check.-->
from X 
<!--***DAN: Shya, make this an autolink to the number of data points - 5930, but should be an autolink, so if the number changes it updates-->

@@

Species-trait data were average species basal metabolic rate (units) and body mass (units) data for X species of birds [@Mcnab_2009] and Y species of mammals [@Mcnab_2008].

@@

@@

<!--***DAN: Shya to add a figure shwoing the locations on a map of the UK and cite it here with an automatic citation-->

>>>>

```{r read_somedata, echo=F, results='hide'}
d_soilCN<-readRDS("Data/RaCA_soilorganicC_soiltotalN_stocks100cm.RDS")
d_birdsBMR<-readRDS("./Data/BMR/BirdBodyMassesMetabolicRates/my_birdsBMR_data.RDS")
d_mammalsBMR<-readRDS("./Data/BMR/MammalianBodyMassesMetabolicRates/my_mammalsBMR_data.RDS")
```

We used datasets that pertain to multiple fields and levels of organization within or related to ecology, including environmental, species-trait, phenological, population, community, and ecosystem functioning data. Copula structure describing the relationship between atmospheric weather variables such as X and Y has been examined previously in the meteorological literature (e.g., REF). We therefore examined environmental variables from the soil instead, using the Rapid Carbon Assessment database (RaCA; @Wills2014).

@@

The database comprises measurements of soil organic carbon and total soil nitrogen (Mg C or N per m$^{2}$ of soil surface) 
<!--***DAN: Shya, this used to say Mg C, but what is Mg? Do you mean mg for miligram? I have written it out, please check and correct if necessary. Also, I added per m^2 of soil surface, please check.
***Shya: Mg means mega gram, So an "Mg C" is a ton of Carbon - the standard SI unit when it comes to talking about soil Carbon measurement.-->
from `r nrow(d_soilCN)` 
<!--***DAN: Shya, make this an autolink to the number of data points - 5930, but should be an autolink, so if the number changes it updates
***Shya: Done.-->

@@

Species-trait data were average species basal metabolic rate (KJ per hour) and body mass (gram) data for `r nrow(d_birdsBMR)`  species of birds [@Mcnab_2009] and `r nrow(d_mammalsBMR)`  species of mammals [@Mcnab_2008].

@@

<!--***Shya: These species number for birds and mammals came from the processed data without any NA and -ve(unrealistic) mass, is that okay? 
for example, species of birds [@Mcnab_2009] raw data (the xls file you gave me) shows 712 species out of which some have NA in both mass and BMR column and one entry has -ve mass!!!-->

@@

<!--***DAN: Shya to add a figure shwoing the locations on a map of the UK and cite it here with an automatic citation
***Shya: It is already in suppmat figure S1.-->
